Supplementary Materials for the article \textit{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

### 2017-10-03 regularity.tex
some fixes the initial version

%$$
%C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}|s(l + 1,j)| \ (rk)^j \Ri.
%$$ Derivatives are obtained easily from this form
%$$&=  \sum_{k=i-n + 1}^{\lfloor n - i/2 \rfloor}(i-l+1)c_k + (i-(n-k + 1)+1)c_{n-k+1} 
%\frac{d}{dk}C(n,k) = \sum_{l=0}^{n-1} b_l \Le\sum_{j=1}^{l+1}j \ |s(l + 1,j)| \ k^{j-1}\Ri
%$$and
%$$
%\frac{d}{dk}C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}j \ r^{j} \ |s(l + 1,j)| \ k^{j-1}\Ri.
%$$
\section{Terms $a_j$ sum to one}
\begin{align*}
\sum_{j=1}^{n}a_j &=\sum_{j=1}^{n} \Le \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=1}^{n} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=0}^{l-1} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ (l+1)! \\
& =  \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}}(l+1)
\end{align*}
\end{document}

>>>>

%$$
%C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}|s(l + 1,j)| \ (rk)^j \Ri.
%$$ Derivatives are obtained easily from this form
%$$&=  \sum_{k=i-n + 1}^{\lfloor n - i/2 \rfloor}(i-l+1)c_k + (i-(n-k + 1)+1)c_{n-k+1} 
%\frac{d}{dk}C(n,k) = \sum_{l=0}^{n-1} b_l \Le\sum_{j=1}^{l+1}j \ |s(l + 1,j)| \ k^{j-1}\Ri
%$$and
%$$
%\frac{d}{dk}C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}j \ r^{j} \ |s(l + 1,j)| \ k^{j-1}\Ri.
%$$
\section{Terms $a_j$ sum to one}
\begin{align*}
\sum_{j=1}^{n}a_j &=\sum_{j=1}^{n} \Le \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=1}^{n} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=0}^{l-1} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ (l+1)! \\
& =  \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}}(l+1)
\end{align*}
\section{ML terms}
Assume we have $n$ samples of $X,Y$ and $Z$. We can write the logarithm of the maximized likelihood, $\hat{P}_n(X \mid Y)$, as follows
\begin{align*}
\log \hat{P}_n(X \mid Y) & = -n \Le H_n(X) - I_n(X;Y) \Ri \\
&= -n \  H_n(X\mid Y),
\end{align*}where $I_n(\cdot;\cdot)$ is the empirical mutual information. This implies that the assumption
$$
H_n(X \mid Y) \leq H_n(X \mid Y \cup Z)
$$ is equivalent to
$$
\log \hat{P}_n(X \mid Y) \geq \log \hat{P}_n(X \mid Y \cup Z). 
$$Actually we must have the equality holding in the above expression, since
$$
H_n(X \mid Y) < H_n(X \mid Y \cup Z)
$$ would imply that
$$
I_n(X ; Z \mid Y ) < 0
$$which is impossible.
\end{document}
